Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-05 journal/article.tex
Spell check

Communication and transparency was an important success factor brought up in the
promary studies. The ongoing change should be communicated intensively to
everyone. Transparency and inclusiveness were success factors related to
communication.
Table \ref{table:success_communication} presents success factors relating to
communicating the change.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Communicate the change intensively  &
                P16, P22, P33, P40, P41, P43, P48  \\
        Enable transparency in the change  &
                P6, P11, P16, P42, P43  \\
        Engage people broadly in the organization  &
                P4, P6, P16, P22, P31 \\
        \bottomrule
    \end{tabular}
    \caption{Succes factors relating to communicating the change}
    \label{table:success_communication}
\end{table}

@@

A key principle in agile is to allow development teams decide for themselves how
they execute their tasks. To make te agile model work well teams need to
self-organize, and be allowed to make decisions on the pace of development.
When teams can perform their tasks autonomically the transformation towards
agile will progress.
Table \ref{table:success_autonomy} lists success factors relating to autonomy of
development teams.

@@

A few succes factors which did not fit in the above categories stood out. These
success factors are creating a positive experience in the beginning, arranging
socaial events, emphasizing principles over mechanics, and the previous
organizational culture being like agile.

>>>>

Communication and transparency was an important success factor brought up in the
primary studies. The ongoing change should be communicated intensively to
everyone. Transparency and inclusiveness were success factors related to
communication.
Table \ref{table:success_communication} presents success factors relating to
communicating the change.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Communicate the change intensively  &
                P16, P22, P33, P40, P41, P43, P48  \\
        Enable transparency in the change  &
                P6, P11, P16, P42, P43  \\
        Engage people broadly in the organization  &
                P4, P6, P16, P22, P31 \\
        \bottomrule
    \end{tabular}
    \caption{Success factors relating to communicating the change}
    \label{table:success_communication}
\end{table}

@@

A key principle in agile is to allow development teams decide for themselves how
they execute their tasks. To make the agile model work well teams need to
self-organize, and be allowed to make decisions on the pace of development.
When teams can perform their tasks autonomically the transformation towards
agile will progress.
Table \ref{table:success_autonomy} lists success factors relating to autonomy of
development teams.

@@

A few success factors which did not fit in the above categories stood out. These
success factors are creating a positive experience in the beginning, arranging
social events, emphasizing principles over mechanics, and the previous
organizational culture being like agile.
